### 2014-07-09 Paper_v1.tex
Small update

The rule based regulatory strategy captured classic patterns of allosteric activation and inhibition of enzyme activity (Fig. \ref{fig-kinetics-simulations}).

End product yield was controlled by feedback inhibition, while selectivity was controlled by branch point enzyme inhibition (Fig. \ref{fig-onoff-simulations}).
A critical test of our modeling approach was to simulate networks with known behavior. If we cannot reproduce simple network expected behavior, then our
modeling strategy, and particularly the rule-based approximation of allosteric regulation, will not be feasible for large scale problems.
We considered two cases,  control on/off, for each network configuration. 
Each of these cases had identical kinetic parameters and initial conditions; 
the \textit{only} differences between the cases was the allosteric regulation rules, and the control parameters associated with these rules. 
As expected, end product accumulation was larger for network A when the control was off (no feedback inhibition of $E_{1}$ by $P_{1}$ and $P_{2}$),
as compared to the on case (Fig. \ref{fig-onoff-simulations}A). We found this behavior was robust to the choice of underlying kinetic parameters, 
as we observed that same qualitative response across an ensemble of randomized parameter sets (N = 100). 
The control on/off response of network B was more subtle. In the off case, the behavior was qualitatively similar to network A. 
However, for the on case, flux was diverted away from $P_{2}$ formation by feedback inhibition of $E_{6}$ activity at the $M_{2}$ branch point by $P_{1}$ (Fig. \ref{fig-onoff-simulations}B).
Lower $E_{6}$ activity at the $M_{2}$ branch point allowed more flux toward $P_{1}$ formation, hence the yield of $P_{1}$ also increased (Fig. \ref{fig-onoff-simulations}C).
Again, the control on/off behavior was robust to the values of the kinetic parameters, as the same qualitative trend was conserved across 
an ensemble of possible randomized kinetic parameters (N = 100). Taken together, these simulations suggested that the rule based allosteric control 
concept could robustly capture expected feedback behavior.

>>>>

The rule based regulatory strategy captured classic patterns of allosteric activation and inhibition of enzyme activity (Fig. \ref{fig-kinetics-simulations}).  
The first case we explored was substrate activation of enzyme activity (positive cooperativity). 
Classically, we expected a sigmoidal relationship substrate abundance and reaction rate for positive cooperativity.

End product yield was controlled by feedback inhibition, while selectivity was controlled by branch point enzyme inhibition (Fig. \ref{fig-onoff-simulations}).
A critical test of our modeling approach was to simulate networks with known behavior. If we cannot reproduce the expected behavior of simple networks, then our
modeling strategy, and particularly the rule-based approximation of allosteric regulation, will not be feasible for large scale problems.
We considered two cases,  control on/off, for each network configuration. 
Each of these cases had identical kinetic parameters and initial conditions; 
the \textit{only} differences between the cases was the allosteric regulation rules, and the control parameters associated with these rules. 
As expected, end product accumulation was larger for network A when the control was off (no feedback inhibition of $E_{1}$ by $P_{1}$ and $P_{2}$),
as compared to the on case (Fig. \ref{fig-onoff-simulations}A). We found this behavior was robust to the choice of underlying kinetic parameters, 
as we observed that same qualitative response across an ensemble of randomized parameter sets (N = 100). 
The control on/off response of network B was more subtle. In the off case, the behavior was qualitatively similar to network A. 
However, for the on case, flux was diverted away from $P_{2}$ formation by feedback inhibition of $E_{6}$ activity at the $M_{2}$ branch point by $P_{1}$ (Fig. \ref{fig-onoff-simulations}B).
Lower $E_{6}$ activity at the $M_{2}$ branch point allowed more flux toward $P_{1}$ formation, hence the yield of $P_{1}$ also increased (Fig. \ref{fig-onoff-simulations}C).
Again, the control on/off behavior was robust to the values of the kinetic parameters, as the same qualitative trend was conserved across 
an ensemble of possible randomized kinetic parameters (N = 100). Taken together, these simulations suggested that the rule based allosteric control 
concept could robustly capture expected feedback behavior.
